\documentclass[a4paper,10pt]{article}

\usepackage{url}
\usepackage{parskip}
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage[margin=0.55cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[unicode]{hyperref}

\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\definecolor{headblue}{rgb}{0.1,0.22,0.42}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

\titleformat{\section}{\normalsize\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{4pt}{3pt}

\setlist[itemize]{nosep, leftmargin=1.2em, itemsep=0.5pt, label={$\cdot$}}
\setlength{\parskip}{0pt}

\begin{document}
\pagestyle{empty}

% ── HEADER ──
\begin{center}
  {\Large\textbf{\color{headblue}Vasu Manocha}}\\[2pt]
  \small St.\ John's, NL, Canada \;|\; \href{mailto:vmanocha@mun.ca}{vmanocha@mun.ca} \;|\; +1-437-424-7769 \;|\; \href{https://vasumanocha.com}{\textbf{Portfolio}} \;|\; \href{https://github.com/vm1610}{\textbf{GitHub}} \;|\; \href{https://www.linkedin.com/in/vasu-manocha-922b91223/}{\textbf{LinkedIn}}
\end{center}

\vspace{-4pt}

% ── SUMMARY ──
\section{Summary}
\small
Software Engineer with experience shipping \textbf{LLM-powered platforms, REST APIs, and full-stack applications} to production. Led delivery of AI tools used by \textbf{2,000--3,000 HR professionals across 4 countries}; independently built and launched \textbf{FitAccess} to 2,000+ active users. Strong across the backend (Python, FastAPI, AWS) and full-stack (TypeScript, Next.js, Flutter). Seeking Software Engineering roles in Canada.

% ── WORK EXPERIENCE ──
\section{Work Experience}

\noindent\textbf{Software Engineer} \hfill \textit{\small Jan 2025 -- Mar 2026}\\
\textit{\small Apexon}
\begin{itemize}
  \item Built and shipped the \textbf{JD Optimizer Agent} end-to-end: LLM-powered platform adopted by \textbf{2,000--3,000 HR professionals across 4 countries} to automate job description rewrites, skill extraction, bias detection, and tone calibration.
  \item Architected a \textbf{serverless AWS backend} (Lambda, API Gateway, S3, DynamoDB) with FastAPI and reusable REST API patterns, supporting multiple internal AI tools simultaneously.
  \item Delivered the \textbf{Interview Prep Agent} from design to deployment; led as \textbf{Squad Leader} for the Data Fellowship 2025 cohort -- coordinated technical planning and an 8-week agile program for 10+ participants.
\end{itemize}

\vspace{1pt}
\noindent\textbf{Undergraduate Teaching Assistant} \hfill \textit{\small Jan 2023 -- Dec 2024}\\
\textit{\small Memorial University of Newfoundland}
\begin{itemize}
  \item Supported 100+ students per semester across CS and Mathematics courses; held weekly office hours and provided written feedback on assignments.
\end{itemize}

\vspace{1pt}
\noindent\textbf{Undergraduate Research Assistant} \hfill \textit{\small May 2023 -- Sep 2023}\\
\textit{\small Memorial University of Newfoundland}
\begin{itemize}
  \item Co-authored a \textbf{novel theorem} on the Cops \& Robbers problem on directed circulant graphs, producing original proofs for academic publication. \href{https://vasumanocha.com/circulant_graphs_cops_robbers.pdf}{[Paper $\nearrow$]}
\end{itemize}

\vspace{1pt}
\noindent\textbf{Software Developer Intern} \hfill \textit{\small Jun 2021 -- Jul 2021}\\
\textit{\small Konverse.ai}
\begin{itemize}
  \item Developed enterprise chatbots in Python and Dialogflow, automating customer-support flows and integrating third-party APIs to reduce manual handling time.
\end{itemize}

% ── PROJECTS ──
\section{Projects}

\noindent\textbf{FitAccess -- Global Gym Discovery Platform} \hfill \textit{\small 2024--2026}
\begin{itemize}
  \item Built and launched a full-stack gym discovery app with geolocation search, real-time availability, and Google Maps API integration -- reached \textbf{2,000+ active users}.
  \item Stack: \textbf{Next.js, TypeScript, FastAPI, PostgreSQL, Docker, Maps API}. \quad \href{https://fitaccess-global-hub-web-g8rq.vercel.app/}{\textbf{[Live Site $\nearrow$]}}
\end{itemize}

\vspace{1pt}
\noindent\textbf{Whatchu Cooking? -- Social Recipe App} \hfill \textit{\small 2025}
\begin{itemize}
  \item Built a cross-platform mobile app for social recipe sharing and potluck planning in a 4-person agile team; implemented voice-to-text input, Firebase Cloud Storage, Cloud Firestore sync, and Firebase Auth. Stack: \textbf{Flutter, Dart, Firebase, Riverpod}. \quad \href{https://youtu.be/VXxmrGYtY_g}{\textbf{[Demo Video $\nearrow$]}}
\end{itemize}

\vspace{1pt}
\noindent\textbf{2D Game Engine \& Platformer (C++)} \hfill \textit{\small 2025}
\begin{itemize}
  \item Engineered a complete 2D game engine from scratch: entity-component-system (ECS) architecture, real-time physics simulation, enemy AI, and an interactive level editor. \quad \href{https://youtu.be/HgRQLTaYomY}{\textbf{[Demo Video $\nearrow$]}}
\end{itemize}

\vspace{1pt}
\noindent\textbf{Selected Projects}
\begin{itemize}
  \item \textbf{eVerify Email Validator}: Combines regex parsing and live SMTP checks to detect format errors and non-existent domains in real time. \quad \href{https://vm1610.github.io/everify/}{\textbf{[Live Site $\nearrow$]}} \href{https://github.com/vm1610/everify}{\textbf{[GitHub $\nearrow$]}}
  \item \textbf{Lucy Voice Assistant}: Fully offline NLP-powered assistant using speech recognition and natural language command parsing; used internally at Apexon. \quad \href{https://github.com/vm1610/lucy-voice-assistant}{\textbf{[GitHub $\nearrow$]}}
  \item \textbf{Face Recognition Model}: Python + OpenCV system with real-time face and eye detection; built for automated attendance tracking. \quad \href{https://huggingface.co/spaces/vmanocha/face_recognition}{\textbf{[Live Demo $\nearrow$]}} \href{https://github.com/vm1610/face-recognition}{\textbf{[GitHub $\nearrow$]}}
  \item \textbf{Netflix Clone}: Pixel-accurate Netflix UI replica built with vanilla HTML, CSS, and JavaScript -- no frameworks, no shortcuts. \quad \href{https://vm1610.github.io/netflix-clone/}{\textbf{[Live Site $\nearrow$]}}
\end{itemize}

% ── TECHNICAL SKILLS ──
\section{Technical Skills}
\begin{itemize}
  \item \textbf{Languages:} Python, TypeScript, JavaScript, Dart, Java, C++, SQL, HTML, CSS
  \item \textbf{Backend \& APIs:} FastAPI, REST APIs, system design, data structures and algorithms, PostgreSQL, Redis, Postman
  \item \textbf{Cloud \& DevOps:} AWS (Lambda, API Gateway, S3, DynamoDB), Docker, GitHub Actions (CI/CD), Git
  \item \textbf{AI \& Data:} LLM prompt engineering, LangChain, RAG pipelines, multi-agent systems, data preprocessing, model evaluation
  \item \textbf{Frontend \& Mobile:} Next.js, React, Flutter, Firebase (Auth, Firestore, Cloud Storage), Riverpod, responsive web design
  \item \textbf{AI Dev Tools:} Claude Code, Cursor, v0, Lovable, Bolt.new
\end{itemize}

% ── EDUCATION ──
\section{Education}
\noindent\textbf{B.Sc. Computer Science \& Applied Mathematics} \hfill \textit{\small Dec 2025}\\
\textit{\small Memorial University of Newfoundland, St.\ John's NL} \hfill \small GPA: 3.86\,/\,4.00

% ── ACHIEVEMENTS ──
\section{Achievements}
\begin{itemize}
  \item Dean's List -- 2023--2024 \& 2024--2025, Memorial University of Newfoundland
  \item Vedic Maths National 1\textsuperscript{st} Rank (Aug 2021)
\end{itemize}

\end{document}
